One more attempt on ArXe

### 2015-09-30 exp_results.tex
experimental outer valence spectra added, order of sections changed

>>>>

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_1.pdf}
 \caption{
 Outer valence spectra of mixed Ar-Xe clusters, in comparison to the pure species. Panel a) shows the outer valence region of homogeneous Ar and Xe clusters, respectively (see text for details). The two lower panels show the spectra of the mixed species of different size. Sharp lines marked `m' result from photoionization of uncondensed atoms into the Ar 3p$_{1/2,3/2}$ and Xe 5p$_{1/2,3/2}$ final states. Labels in panels b) and c) give the Xe content in the expanding gas mixture, which is lower then the Xe content observed in the heterogeneous clusters. Parts of the spectrum resulting from the Xe inventory of the clusters are shown in blue colour. The photon energy used was 17~eV, apart from the pure Xe cluster spectrum (60 eV).
}
 \label{figure:oval1}
\end{figure}

\begin{figure}[ht]
 \centering
 \includegraphics[width=8.5cm]{pics/figure_oval_2.pdf}
 \caption{
Outer valence spectra of mixed Ar-Xe clusters from gas mixtures with different Xe concentration. See Fig.\ \ref{figure:oval1} and text for details.
}
 \label{figure:oval2}
\end{figure}
